It takes several years for this thesis to come out, and it cannot be there without the support from numerous people. First, I would like to thank my supervisor Dr. Aksel Hallin. As an experienced experimental physicist, he is unique in mastering the art of particle physics experiments and is always on the front line of the research, which amazes people. He is a great teacher with insights and patience. Thanks to Dr. Carsten B. Krauss, who provided me with critical suggestions for my research and also a chance for working in the laboratory. Thanks to Dr. Juan Pablo Y\'{a}\~{n}ez Garza, who shared his smart ideas for physics analysis, and extensive knowledge in neutrinos. 

The research presented in this thesis cannot proceed without the SNO+ collaboration. I would like to thank the whole SNO+ collaboration as well as the staff in SNOLAB. I would like to thank Drs. Jeff Tseng, Edward Leming, and Nuno Barros for giving useful suggestions on the event reconstruction and their help in implementing the codes. I would like to thank Dr. Alex Wright and Brian Krar for their suggestions on the solar neutrino analysis. I am grateful to Drs. Christine Kraus, Erica Caden, Aleksandra Bialek, and Mrs. Nancy Brown, for their roles in arranging and helping my site work in SNOLAB.

Fellow researchers, postdocs, and staff in the Department of Physics at the University of Alberta offered me a lot of help during my Ph.D. study. I would like to thank Drs. Kalpana Singh, David J. Auty, Karin Gilje, Yang Zhang, Fady Shaker, and Munish Sharma for their invaluable help and suggestions. I am grateful to Dr. Kalpana Singh, who gave me a hand when I was first involved in the SNO+ research. Though she was always busy, she generously offered her time to teach me a lot of research methods and shared her smart ideas on resolving problems. Karin and David kindly helped me in the experiment, analyses, and academic English writing as well. I had a wonderful trip to Sudbury with David for my first summer visit to SNOLAB. Thanks to Prof. John Wilson, who helped me with my thesis writing. I am also amazed by his pure enthusiasm for physics. I would like to thank Dr. Richard Soluk, Paul Davis, and Len Wampler for their help in the laboratory. Jamie Rajewski provided technical support on the Compute Canada computing resources, and I am appreciative of his help. For my Ph.D. program, I also received valuable suggestions and help from the faculty and staff, and I would like to thank Drs. Erik Rosolowsky and Craig Heinke, Mrs. Rae Beaumont, Mrs. Suzette Chan, and Mrs. Sarah MacKinnon.

I would like to thank my office mates: Logan Sibley, Pawel Mekarski, Courtney Mielnichuk, Thomas McElroy, Jonathan Chalaturnyk, Joseph Willis, and Pooja Nolan. I spent a wonderful time with these smart and interesting people, who have great enthusiasm for science and life. Logan and Pawel were also my colleagues in SNO+. They kindly helped me to get familiar with the collaboration and research, gave me suggestions in studies and writing, and let me enjoy life in Edmonton.

I am grateful to my friends: Yu Chen, Xuemeng Chen, Jingyan Hao, Dinglian Kang, Jinyuan Luo, Youfang Luo, Yuxiu Lv, Chengyue Qian, Wenhui Ruan, Mingcheng Tang, Haifeng Xu, Wenqing Yu, Lingjun Zhou, and Gaofei Zhu. They have brought me countless interesting insights and ideas about science and life.

When I first came to Edmonton, Prof. Keumhee Chough kindly provided me with accommodation, welcomed me at the airport, and helped me to get familiar with life in the city. I will never forget her kindness.

My parents highly encourage and support me to pursue a postgraduate education abroad. Raising a child is no easier than the Labours of Heracles. I am grateful to my late grandma, who shared her love and always missed me when I was far away from home.
